Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Edit

We now assess the performance impact and responsiveness of
multitasking between a long-running cooperative kernel and a series of
short, non-cooperative kernel launches.  Performance is measured by
comparing the time for multitasked execution with the time taken to
perform all kernel launches in sequence.  Responsiveness, i.e.\ how
fast a non-cooperative kernel can be scheduled, depends not only on
the scheduler implementation, but also on how often the cooperative
kernel offers workgroups to be killed.

@@

\myfiglong\ref{fig:fine-grained-timing} reports, on three
configurations, the gather and execution time of the non-cooperative
kernel w.r.t. the quantity of workgroups allocated to it. 
\ADComment{Not clear: are the times for light and heavy averages?} A logarithmic
scale is used for time since gather times tend to be much smaller than
execution times. The horizontal grey lines indicates the desired period
for non-cooperative kernels.  These graphs show a representative sample of our results; the full set of graphs for all configurations is provided in Appendix~\ref{appendix:extraresponsiveness} (supplementary material).

>>>>

We now assess the responsiveness of multitasking between a long-running cooperative kernel and a series of
short, non-cooperative kernel launches, and the performance impact of multitasking on the cooperative kernel.

@@

\myfiglong\ref{fig:fine-grained-timing} reports, on three
configurations, the average gather and execution times for the non-cooperative
kernel w.r.t. the quantity of workgroups allocated to it.
A logarithmic
scale is used for time since gather times tend to be much smaller than
execution times. The horizontal grey lines indicates the desired period
for non-cooperative kernels.  These graphs show a representative sample of our results; the full set of graphs for all configurations is provided in Appendix~\ref{appendix:extraresponsiveness} (supplementary material).
